---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(opinion.classifier)
options(width = 90)
```

# opinion.classifier

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/opinion.classifier)](https://CRAN.R-project.org/package=opinion.classifier)
[![Travis build status](https://travis-ci.org/mkearney/opinion.classifier.svg?branch=master)](https://travis-ci.org/mkearney/opinion.classifier)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mkearney/opinion.classifier?branch=master&svg=true)](https://ci.appveyor.com/project/mkearney/opinion.classifier)
<!-- badges: end -->

A machine learning classification model for measuring opinion, or editorial, 
content in news text. The model was trained using editorial and news content 
from highly regarded, well-known journalism outlets.

## Installation

You can install the released version of opinion.classifier from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("opinion.classifier")
```

or the development version from Github

``` r
remotes::install_github("mkearney/opinion.classifier")
```


## Example

Get opinion probability estimate 

```{r, eval=FALSE}
opinion.classifier::opinion_score(x)
```
